Import and Tidy ADFG Supplied Location and Haul-out Data

### 2021-06-25 data_raw/adfg/adfg_tidydata.Rmd
CONT TO INCORPORATE RAW DATA FROM ADFG/NSB
a large collection of code and data updates as we work to fully incoporate data share from ADFG and NSB

```{r}
adfg_deployments <- adfg_deployments %>% 
  dplyr::rename(deployid = DeployIDs,
                mapid = MapID,
                date_tagged = DateTagged,
                primary_tag_type = PrimaryTagType,
                flipper_tag_type = FlipperTagType
                ) %>% 
  dplyr::rename_all(tolower) %>% 
  dplyr::mutate(species = tolower(species),
                age = tolower(age),
                sex = tolower(sex)) %>% 
  tidyr::gather(tag_position, tag_type, c(primary_tag_type,flipper_tag_type)) %>% 
  dplyr::mutate(tag_position = ifelse(tag_position == "primary_tag_type",
                   "primary","flipper")) %>% 
  dplyr::filter(!is.na(tag_type)) %>% 
  dplyr::arrange(date_tagged,deployid)

@@

```{r}
adfg_locations <- adfg_locations %>% 
  dplyr::rename(deployid = DeployID,
                location_quality = LocationQuality,
                date_time = Date,
                tag_type = TagType) %>% 
  dplyr::filter(location_quality != "Z") %>% 
  dplyr::select(-MonthNumb) %>% 
  dplyr::rename_all(tolower)

@@

locs_sf <- adfg_locations %>% 
  dplyr::left_join(adfg_deployments, by = c("deployid","tag_type")) %>% 
  sf::st_as_sf(coords = c("longitude","latitude")) %>% 
  sf::st_set_crs(4326) %>% sf::st_transform(3571)

ggplot() +
  annotation_spatial(world, 
                     size = 0, 
                     fill = "grey70") +
  layer_spatial(
    data = locs_sf, size = 0.125
  ) +
  facet_grid(~ species) +
  theme(legend.position = "bottom") +
  ggtitle("ADFG Locations (Argos)",
            subtitle = "all locations from bearded, ringed, and spotted seals")

@@

```{r}
adfg_timelines <- readr::read_csv('ADFG_SealTimelineData3.csv')
```

@@

adfg_timelines <- readr::read_csv('ADFG_SealTimelineData3.csv',
                                  col_types = adfg_timeline_cols) %>% 
  dplyr::mutate(GMTDate = as.Date(GMTDate, origin = "1899-12-30", 
                                     tz = "UTC") %>% 
                  lubridate::as_datetime(),
                Ptt = as.integer(Ptt),
                TagType = toupper(TagType)) %>% 
  dplyr::rename(deployid = DeployIDs,
                tag_type = TagType,
                hist_type = HistType,
                date_time = GMTDate) %>% 
  dplyr::rename_all(tolower) %>% 
  dplyr::select(-c(monthnumb,latitude,longitude,locationquality,sum,hist_type))

@@

adfg_timelines <- adfg_timelines %>% 
        tidyr::gather(bin, percent_dry, starts_with('bin')) %>%
        dplyr::left_join(bins, by = "bin") %>%
        dplyr::mutate(date_time = date_time + lubridate::hours(hour),
                      data_date = lubridate::floor_date(date_time,"day")) %>%
        dplyr::select(c(deployid,ptt,tag_type,date_time,data_date,percent_dry)) %>% 
        dplyr::arrange(deployid,date_time)
```

>>>>

```{r}
adfg_deployments <- adfg_deployments %>% 
  dplyr::rename(speno = DeployIDs,
                mapid = MapID,
                deploy_dt = DateTagged,
                primary_tag_type = PrimaryTagType,
                flipper_tag_type = FlipperTagType
                ) %>% 
  dplyr::rename_all(tolower) %>% 
  dplyr::mutate(species = tolower(species),
                age = tolower(age),
                sex = tolower(sex)) %>% 
  tidyr::gather(tag_position, tag_family, c(primary_tag_type,flipper_tag_type)) %>% 
  dplyr::mutate(tag_position = ifelse(tag_position == "primary_tag_type",
                   "primary","flipper")) %>% 
  dplyr::filter(!is.na(tag_family)) %>% 
  dplyr::arrange(deploy_dt)

@@

```{r}
adfg_locations <- adfg_locations %>% 
  dplyr::rename(speno = DeployID,
                quality = LocationQuality,
                locs_dt = Date,
                tag_family = TagType) %>% 
  dplyr::filter(quality != "Z") %>% 
  dplyr::select(-MonthNumb) %>% 
  dplyr::rename_all(tolower) %>% 
  dplyr::left_join(adfg_deployments, by = c("speno","tag_family")) %>% 
  mutate(species_code = case_when(
        species == "bearded" ~ "EB",
        species == "ribbon" ~ "HF",
        species == "spotted" ~ "PL"
    )) %>% 
    mutate(deployid = glue::glue("{species_code}",
                            "{lubridate::year(deploy_dt)}_{ptt}")) %>% 
    mutate(unique_day =
             glue::glue("{lubridate::year(locs_dt)}",
                  "{lubridate::yday(locs_dt)}",
                  .sep = "_")) %>% 
  select(-species_code) %>% 
  relocate(deployid,ptt) %>% 
  filter(species %in% c('bearded', 'ribbon', 'spotted')) %>%
    filter(lubridate::month(locs_dt) %in% c(3,4,5,6,7)) %>%
  sf::st_as_sf(coords = c("longitude","latitude")) %>% 
  sf::st_set_crs(value = "EPSG:4326")

@@

ggplot() +
  annotation_spatial(world, 
                     size = 0, 
                     fill = "grey70") +
  layer_spatial(
    data = sf::st_transform(adfg_locations,3571), size = 0.125
  ) +
  facet_grid(~ species) +
  theme(legend.position = "bottom") +
  ggtitle("ADFG Locations (Argos)",
            subtitle = "all locations from bearded, ringed, and spotted seals")

@@

```{r}
adfg_timelines <- readr::read_csv(here::here('data_raw/adfg/ADFG_SealTimelineData3.csv'))
```

@@

adfg_timelines <- readr::read_csv(here::here('data_raw/adfg/ADFG_SealTimelineData3.csv'),
                                  col_types = adfg_timeline_cols) %>% 
  dplyr::mutate(GMTDate = as.Date(GMTDate, origin = "1899-12-30", 
                                     tz = "UTC") %>% 
                  lubridate::as_datetime(),
                Ptt = as.integer(Ptt),
                TagType = toupper(TagType)) %>% 
  dplyr::rename(speno = DeployIDs,
                tag_family = TagType,
                hist_type = HistType,
                timeline_start_dt = GMTDate) %>% 
  dplyr::rename_all(tolower) %>% 
  dplyr::left_join(adfg_deployments, by = c("speno","tag_family")) %>% 
  mutate(species_code = case_when(
        species == "bearded" ~ "EB",
        species == "ribbon" ~ "HF",
        species == "spotted" ~ "PL"
    )) %>% 
  mutate(deployid = glue::glue("{species_code}",
                            "{lubridate::year(deploy_dt)}_{ptt}")) %>%
  mutate(unique_day =
             glue::glue("{lubridate::year(timeline_start_dt)}",
                  "{lubridate::yday(timeline_start_dt)}",
                  .sep = "_")) %>%
  dplyr::relocate(deployid) %>% 
  filter(species %in% c('bearded', 'ribbon', 'spotted')) %>%
    filter(lubridate::month(timeline_start_dt) %in% c(3,4,5,6,7)) %>%
  dplyr::select(-c(monthnumb,latitude,longitude,locationquality,sum,hist_type))

@@

adfg_timelines <- adfg_timelines %>% 
        tidyr::gather(bin, percent_dry, starts_with('bin')) %>%
        dplyr::left_join(bins, by = "bin") %>%
        dplyr::mutate(timeline_start_dt = timeline_start_dt + lubridate::hours(hour)) %>%
        dplyr::select(c(deployid,speno,species,age,sex,deploy_dt,ptt,tag_family,timeline_start_dt,unique_day,percent_dry)) %>% 
        dplyr::arrange(deployid,timeline_start_dt)
```
